Turkey Hemorrhagic Enteritis Virus transcription profiling

### 2023-03-17 README.Rmd
Update Project README.Rmd

```{r include = FALSE}

script_dir <- for(item in list.files("scripts")){
    print(item, quote = FALSE)}

rawfiles_dir <- for(item in list.files("raw_files")){
    print(item, quote = FALSE)}

results_dir <- for(item in list.files("results")){
    print(item, quote = FALSE)
}
```
* **`ROOT (thev_transcriptome)`**
    * **Directories:**
        * *`scripts`*
        * *`raw_files`*
        * *`results`*
        * *`trimmedReads`*
    * **Files**
        * *`Snakefile`*
        * *`driver_script`* - *`deprecated`*
        * *`README.Rmd`*
        * *`project_map.pdf`* 
        * *`project_jobmap.pdf`*
        * *`thev_transcriptome.Rproj`* - *not on Git*
    * **Hidden files**
        * `.gitignore`
        * `.Rproj.user` - *not tracked*
        * `.snakemake` - *not tracked*

>>>>

```{r list_dirs, exclude=TRUE}

script_dir <- list.files("scripts")
rawfiles_dir <- list.files("raw_files")
results_dir <- list.files("results")
reads_dir <- list.files("trimmedReads")

```
* **`ROOT (thev_transcriptome)/`**
    * **Directories:**
        * *`raw_files`/* - Add README for more details
            * ``r rawfiles_dir[1]`/`
            * ``r rawfiles_dir[2]`/`
            * ``r rawfiles_dir[3]`/`
        * *`results/`* - Add README for more details
            * ``r results_dir[1]`/`
            * ``r results_dir[2]`/`
            * ``r results_dir[3]`/`
        * *`scripts/`* - Add README for more details
            * ``r script_dir[1]`/`
            * ``r script_dir[2]`/`
            * ``r script_dir[3]`/`
        * *`trimmedReads/`* - Add README for more details
            * ``r reads_dir[1]`/`
            * ``r reads_dir[2]`/`
    * **Files**
        * *`Snakefile`*
        * *`driver_script`* - *`deprecated`*
        * *`README.html`*
        * *`README.Rmd`*
        * *`project_map.svg`* 
        * *`project_jobmap.svg`*
        * *`thev_transcriptome.Rproj`* - *not on Git*
    * **Hidden files**
        * `.gitignore`
        * `.Rproj.user` - *not on Git*
        * `.snakemake` - *not on Git*

`r script_dir`
